Holomorphic field theories and higher algebra

### 2022-11-29 draft.tex
su(2)

\def\g{{\mathfrak g}}
\def\U{{\rm U}}
\def\mc{\mathcal}
\def\mcol{\, | \,}
\def\ot{\otimes}
\def\Disj{\operatorname{Disj}}
\def\Open{\operatorname{Open}}
\def\Vect{\operatorname{Vect}}
\def\jou{{\mathtt{j}}}
\def\bgamma{{\mathbf{\gamma}}}
\def\bbeta{{\mathbf{\beta}}}
\def\CDO{{\cC\cD}}
\def\SU{{\rm SU}}
\def\sfa{\mathsf{a}}
\def\del{\partial}
\def\til{\Tilde}
\def\Sol{\text{Sol}}
\def\Spec{\text{Spec}}

@@

There will be two theories. 
We call one side {\em electric} and the other {\em magnetic}.

\begin{dfn}
Fix a positive integer $F$, for flavor, and fix integers $N$ and $\check{N}$ such that $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.

The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors and {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.
We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.

The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
(and $\check{\nu}$ for the partner field to $\check{\mu}$).
We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
\owen{Please double-check that formula.}
\end{dfn}

@@

@@

As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{Whol}.
There are then two further pieces of evidence when these quantum theories are examined:
\begin{enumerate}
\item[(2)] There are {\em flavor} symmetries by $SL(F)$ that act on the quarks and antiquarks of each theory, 
and these can be matched under the duality. 
For the classical holomorphic theories, these symmetries enhance to an action of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
Under quantization, these have isomorphic anomalies.
\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and these can be matched under duality.
\end{enumerate}
This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
We now turn to fleshing out these assertions.

@@

In the electric case there are $N$ such diagrams, with all the internal edges are labeled by $Q-R$ propagators. 
This gives rise to the local anomaly
\beqn\label{eqn:electricflavor}
 \frac{N}{16} \int \op{tr}_{\underline{F}} \left(\sfa \, \partial \sfa \, \partial \sfa\right) 
\eeqn
where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.

The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: 
\begin{itemize}
\item[(a)] those with  internal edges labeled by $\check{Q}-\check{R}$ propagators and 
\item[(b)] those will internal edges labeled by $\check{\mu}-\check{\nu}$ propagators. 
\end{itemize}
There are $\check{N} = F - N$ copies of diagram (a), which gives rise to the term
\[
 \frac{\check{N}}{16} \int \op{tr}_{\underline{F}^*} \left(\sfa \, \partial \sfa \, \partial \sfa\right) .
\]
Here, $\op{tr}_{\underline{F}^*}$ denotes the trace in the dual to the fundamental representation. 
There are $F$ copies of diagram (b), which gives rise to the term
\[
\frac{F}{16}\int \op{tr}_{\underline{F}} \left(\sfa\, \partial \sfa \, \partial \sfa\right).
\]
Since $\op{tr}_{\underline{F}^*} (T^3) = - \op{tr}_{\underline{F}} (T^3)$ for any $T \in \sl(F)$, 
we see that the sum of these two terms agrees with \eqref{eqn:electricflavor} on the electric side.
\end{proof}

@@

@@

>>>>

\def\g{{\mathfrak g}}
\def\U{{\rm U}}
\def\mc{\mathcal}
\def\mcol{\, | \,}
\def\ot{\otimes}
\def\Disj{\operatorname{Disj}}
\def\Open{\operatorname{Open}}
\def\Vect{\operatorname{Vect}}
\def\jou{{\mathtt{j}}}
\def\bgamma{{\mathbf{\gamma}}}
\def\bbeta{{\mathbf{\beta}}}
\def\CDO{{\cC\cD}}
\def\SU{{\rm SU}}
\def\sfa{\mathsf{a}}
\def\del{\partial}
\def\til{\Tilde}
\def\Sol{\text{Sol}}
\def\Spec{\text{Spec}}
\def\C{{\mathbb{C}}}

@@

There will be two holomorphic theories on $\CC^2$. 
We call one side {\em electric} and the other {\em magnetic}.
These turn out to be the twists of the original electric and magnetic supersymmetric theories of the famous Seiberg duality, which justifies our terminology.

\begin{dfn}
Fix a positive integer $F$, for flavor, and fix integers $N$ and $\check{N}$ such that $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
\begin{itemize}
\item
The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors and {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.
We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.
\item
The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ which take values in $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
(and $\check{\nu}$ for the partner field to $\check{\mu}$).
We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
\end{itemize}
\end{dfn}

@@

\subsubsection{The duality functor}

There is a way to define the dual of any supersymmetric QCD theory with mesons that satisfies the following properties:
\begin{itemize}
\item In the case that there are no mesons in the original theory, like in the electric theory, the dual agrees with the magnetic theory.
\item The dual of the magnetic theory is equivalent to the original electric theory.
In other words, the double dual of the electric theory is equivalent to itself. 
\end{itemize}
%In fact, more generally, the double dual of any supersymmetric QCD with mesons returns the same theory (up to equivalence). 
Let us briefly remark how this general duality looks classically in the holomorphic context.

Suppose that we have a holomorphic QCD theory with $N$ colors, $F$ flavors, and with mesons $\mu$ valued in some vector space $V_M$. 
The superpotential is $W(QQ^\dagger, \mu)$.
The dual theory is again a holomorphic QCD theory with mesons.
Precisely the dual theory is holomorphic QCD with $F-N$ colors, $F$ flavors, and mesons valued in 
\beqn
(\mu, \til \mu) \in V_M \oplus \C^{F^2} .
\eeqn
The superpotential of this dual holomorphic QCD theory (whose quarks we label by $\til Q$) is 
\beqn
\til W (\mu, \til \mu, \til Q) = W|_{\til \mu = Q Q^\dagger}(\mu, \til \mu) + \Tr \til{Q}^\dagger \til{\mu} \til{Q} .
\eeqn
Notice that when $V_M = 0, W=0$ this agrees with the dual magnetic theory that we introduced above.

Now, let's suppose we start with the magnetic theory with $F-N$ colors, $F$ flavors, and $F^2$ mesons.
The superpotential is $W = \Tr \check{Q}^\dagger \check{\mu} \check{Q}$. 
Taking the dual of this theory we obtain holomorphic QCD with $N$ colors and $F$ flavors as expected.
However, we have mesons $\check{\mu}$ and $\til \mu$ both valued in $\End(\C^F)$. 
The superpotential is simply
\beqn
\til W = \Tr \check \mu \til \mu + \Tr \til Q^\dagger \check{\mu} \til Q .
\eeqn
The first term arises from substituting $\til \mu = \check Q \check Q^\dagger$ in the original magnetic superpotential. 
This term has the effect of making both $\mu,\check \mu$ massive, and hence they can be integrated out to obtain the original electric theory. 
(In fact, this argument can be upgraded to give an equivalence of BV theories from the electric theory and its double dual.)

@@

As we discuss in a moment, holomorphic QCD can be quantized using the techniques of \cite{Whol}.
There are then two further pieces of evidence when these quantum theories are examined:
\begin{enumerate}
\item[(2)] There are {\em flavor} symmetries by $SL(F)$ that act on the quarks and antiquarks of each theory, 
and these can be matched under the duality. 
For the classical holomorphic theories, these symmetries enhance to an action of infinite-dimensional algebra of holomorphic $\sl(F)$-valued functions on the quark and antiquark fields.
Under quantization, these have isomorphic anomalies.
\item[(3)] There are {\em spacetime} symmetries that act on each theory, notably isometries, and these can be matched under duality.
\end{enumerate}
This triple of evidence is analogous (and sometimes stronger) than results for Seiberg duality for SQCD. 
We now turn to fleshing out these assertions.

@@

In the electric case there are $N$ such diagrams, with all the internal edges are labeled by $Q-R$ propagators. 
This gives rise to the local anomaly
\beqn\label{eqn:electricflavor}
 \frac{N}{16 \pi^2} \int \op{tr}_{\underline{F}} \left(\sfa \, \partial \sfa \, \partial \sfa\right) 
\eeqn
where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.\footnote{The overall analytic coefficient can be explicitly determined, see \cite{GWkm} for related computations.}

The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: 
\begin{itemize}
\item[(a)] those with  internal edges labeled by $\check{Q}-\check{R}$ propagators and 
\item[(b)] those will internal edges labeled by $\check{\mu}-\check{\nu}$ propagators. 
\end{itemize}
There are $\check{N} = F - N$ copies of diagram (a), which gives rise to the term
\[
 \frac{\check{N}}{16 \pi^2} \int \op{tr}_{\underline{F}^*} \left(\sfa \, \partial \sfa \, \partial \sfa\right) .
\]
Here, $\op{tr}_{\underline{F}^*}$ denotes the trace in the dual to the fundamental representation. 
There are $F$ copies of diagram (b), which gives rise to the term
\[
\frac{F}{16\pi^2}\int \op{tr}_{\underline{F}} \left(\sfa\, \partial \sfa \, \partial \sfa\right).
\]
Since $\op{tr}_{\underline{F}^*} (T^3) = - \op{tr}_{\underline{F}} (T^3)$ for any $T \in \sl(F)$, 
we see that the sum of these two terms agrees with \eqref{eqn:electricflavor} on the electric side.
\end{proof}

@@

\subsubsection{$SU(2)$ SQCD}

Let's consider the special case where $N=2$ so that the gauge group on the electric side is $G = SU(2)$. 
In this case, the fundamental and anti-fundamental representations are isomorphic $V_Q = V^*_Q$, so the quarks are valued in
\beqn
(Q, Q^\dagger) \in \Omega^{0,\bu}(\CC^2, V_Q^{\oplus 2}) .
\eeqn
This implies that the flavor symmetry group $SU(F) \times SU(F)$ admits an enhancement to $SU(2F)$.

On the magnetic side, the mesons still take values in the $SU(F) \times SU(F)$ representation
\beqn
V_{\check{M}} = (\CC^F)^* \otimes \CC^F \cong \CC^{\oplus F^2} .
\eeqn
There are $F$ dual quarks $\check{Q}$ transforming in the $SU(F-2)$ fundamental representation and $F$ dual antiquarks $\check{Q}^\dagger$ transforming in the antifundamental representation. 
Again the flavor symmetry group admits an enhancement to $SU(2F)$.

Let's further consider some special cases for small values of flavors.

$\bullet \ul{F=2}$. \brian{I'm confused}

$\bullet \ul{F=3}$. 
In this case the dual gauge group is trivial and we only have quarks, antiquarks, and mesons which together are valued in the following $SU(3) \times SU(3)$ representation
\beqn
(\CC^3)^* \otimes \CC^3 \oplus \CC^3 \oplus (\CC^3)^* .
\eeqn
In a way that is consistent with the flavor symmetry enhancement on the electric side, this representation which appears on the dual magnetic side enhances to the $SU(2 \cdot 3) = SU(6)$ representation $\wedge^2 (\C^6)$, where $\C^6$ is the fundamental $SU(6)$ representation.
If we denote by $\Phi$ the field which combines all magnetic quarks, antiquarks, and mesons, then the classical superpotential can be written in an manifestly $SU(6)$ invariant way as
\beqn
W = \frac16 \Phi \wedge \Phi \wedge \Phi .
\eeqn
We conclude that the magnetic dual holomorphic theory can be expressed in a $SU(6)$ invariant way as a holomorphic $\sigma$-model from $\C^2$ to the (derived) critical locus of $W$. 
The critical locus of $W$ is simply the space of solutions to the equation
\beqn
\Phi \wedge \Phi = 0 \in \wedge^4 (\C^6) .
\eeqn
This description is the affine Pl\"ucker embedding of the affine cone of the Grassmannian~$\text{Gr}(2,6)$.

$\bullet \ul{F=4}$.
This case is special since the gauge group on both sides of Seiberg duality is $SU(2)$. 
On the electric side we have $SU(2)$ gauge theory with $F=4$ flavors. 
On the magnetic side we have $SU(2)$ gauge theory with $F=4$ flavors and mesons which take values in $\C^{4^2} = \C^{16}$.

We have pointed out that for any $F$ the global flavor symmetry group admits an enhancement to $SU(2F)$. 
For $F \geq 4$ the

@@

A duality

The basic two-dimensional supersymmetric theories involved in both sides of this duality are particular gauged linear $\sigma$-models (GLSMs) with $\cN=(2,2)$ supersymmetry. 
The physics terminology for the supersymmetric GLSM is a two-dimensional $\cN=(2,2)$ supersymmetric gauge theory coupled to some number of chiral multiplets transforming in a particular representation.
For gauge group $U(N)$, one takes $F_f$ chiral multiplets valued in the fundamental representation $\CC^N$ and $F_a$ chiral multiplets valued in the anti-fundamental representation.
